---
title: "Motion Estimation"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(viridis)
library(ggplot2)
library(cowplot)
library(extrafont)
library(reshape2)
library(ggplot2)
library(here)
library(emmeans)
library(DT)

library(tidyverse)
loadfonts()
```

## Estimating known motion

```{r read_results}
motion_df <- read.csv("data/motion_benchmark.csv")
qc_df <- read.csv('data/qc_benchmark.csv')

motion_df$was_moved <- !with(motion_df, 
  (true_trans_z == 0) &
  (true_trans_y == 0) &
  (true_trans_z == 0) &
  (true_rot_x == 0) &
  (true_rot_y == 0) & 
  (true_rot_z == 0))

table(motion_df$was_moved)

# Calculate the errors
for (motion_axis in c("x", "y", "z")){
  for (motion_type in c("trans", "rot")){
    est.mov.name <- paste0(motion_type, "_", motion_axis)
    est.mov <- motion_df[est.mov.name]
    if (motion_type == "rot"){
      est.mov <- est.mov * 180 / pi
      motion_df[est.mov.name] <- est.mov
    }
    true.mov <- motion_df[paste0("true_", motion_type, "_", motion_axis)]
    
    error.col <- paste("error", motion_type, motion_axis, sep="_")
    motion_df[error.col] <- true.mov - est.mov
  }
}

# Get only the columns for the motion analysis
motion_columns <- c("bval", "grad_x", "grad_y", "grad_z",
                    "iternum", "scheme", "method", "setting", "percent_motion", "was_moved",
                    "error_trans_x", "error_trans_y", "error_trans_z", "error_rot_x", "error_rot_y", "error_rot_z",
                    "true_trans_x", "true_trans_y", "true_trans_z", "true_rot_x", "true_rot_y", "true_rot_z",
                    "trans_x", "trans_y", "trans_z", "rot_x", "rot_y", "rot_z", "volnum"
                    )
moved <- motion_df[, motion_columns]


m.moved <- melt(moved,
    measure.vars = c("error_trans_x", "error_trans_y", "error_trans_z", "error_rot_x", "error_rot_y", "error_rot_z",
                     "true_trans_x", "true_trans_y", "true_trans_z", "true_rot_x", "true_rot_y", "true_rot_z",
                     "trans_x", "trans_y", "trans_z", "rot_x", "rot_y", "rot_z"))

m.moved$motion.type <- 'Translation'
m.moved$motion.type[grep('rot_', m.moved$variable)] <- 'Rotation'
table(m.moved$motion.type)
m.moved$axis <- gsub(".*_([xyz])$", '\\1', m.moved$variable)
m.moved$source <- "Estimated"
m.moved$source[grep('true', m.moved$variable)] <- "Truth"
m.moved$source[grep('error', m.moved$variable)] <- "Error"
table(m.moved$source)
motion_est_error <- subset(m.moved, source=="Error")
motion_ests <- subset(m.moved, source!="Error")
motion_ests$variable <- NULL
motion.check <- dcast(motion_ests, ... ~ source)
settings.check <- dcast(motion_ests, ... ~ source + setting)

```



## Estimating known motion

```{r cars}


truth <- moved %>%
  select(-matches('grad')) %>%
  select(-starts_with('error_')) %>%
  gather('truth', 'true_values', matches('true')) %>%
  select(-matches('_(x|y|z)'))
  
estimates <- moved %>%
  gather('estimated', 'estimated_values', matches('_(x|y|z)'), -matches('true')) %>%
  select(-matches('true')) %>%
  select(-starts_with('error_')) %>%
  filter(!str_detect(estimated, 'grad'))
```



```{r}
actually.moved <- subset(motion.check, was_moved)

estimates %>%
  cbind(select(truth, matches('tru'))) %>%
  filter(was_moved) 


%>%
  ggplot(., aes(x=true_values, y=estimated_values, color=method, shape=as.factor(percent_motion))) + 
  geom_point(alpha=0.1) + 
  geom_abline(intercept=0, slope=1) + 
#  xlim(-3,3) + ylim(-3,3) +
  facet_grid(motion.type~ axis) +
  ggtitle("Estimated Motion vs. Ground Truth Motion") +
  theme_minimal()


```


## Compare absolute errors between the methods

NOTE: We now have 15 and 30% motion. 50% is being run now.

```{r}
theme_set(theme_cowplot())
# Embed the fonts

actually.moved$error <- with(actually.moved, Truth - Estimated)
comparable <- subset(actually.moved, scheme %in% c('HCP', 'ABCD'))

ss10 <- ggplot(subset(comparable, percent==10), aes(x=error, fill=method)) + 
  geom_histogram(alpha=0.6, position="identity") +
  facet_grid(scheme~motion.type, scales = "free_y") +
  theme_cowplot(12)

ss25 <- ggplot(subset(comparable, percent==25), aes(x=error, fill=method)) + 
  geom_histogram(alpha=0.6, position="identity") +
  facet_grid(scheme~motion.type, scales = "free_y") +
  theme_cowplot(12)

plot_grid(ss10, ss25, labels = c('A', 'B'), label_size = 12)
  

```

```{r}
comparable <- subset(actually.moved, scheme %in% c('DSIQ5', 'HASC55'))

ss10 <- ggplot(subset(comparable, percent==10), aes(x=error, fill=scheme)) + 
  geom_density(alpha=0.6, position="identity") +
  facet_grid(.~motion.type, scales = "free_y") +
  theme_cowplot(12)

ss25 <- ggplot(subset(comparable, percent==25), aes(x=error, fill=scheme)) + 
  geom_density(alpha=0.6, position="identity") +
  facet_grid(.~motion.type, scales = "free_y") +
  theme_cowplot(12)

plot_grid(ss10, ss25, labels = c('A', 'B'), label_size = 12)
  

```

# Stat Tests

Here we test difference of variance between the absolute error of each parameter setting.

First, calculate absolute error for each estimation, then group by the parameters and nest this dataframe, giving one row of parameters with a nested df of absolute errors using these settings:
```{r}
grouped_absolute_err <- motion.check %>% 
  mutate(error = Estimated - Truth) %>% 
  mutate(abs_error =  abs(error)) %>%
  group_nest(scheme, method, percent, was.moved, motion.type) %>%
  crossing(.,.)

grouped_absolute_err <- grouped_absolute_err %>%
  filter(
    #scheme == scheme1 &
      method != method1 &
      percent == percent1 &
      was.moved == TRUE &
      was.moved1 == TRUE &
      motion.type == motion.type1
    ) %>%
  arrange_at(vars(-data, -data1))

grouped_absolute_err
```

Then, loop through each line of the absolute errors. For each line, compare the data using a nonparametric permutation T-test:
```{r, warning=FALSE, message=FALSE, cache=TRUE}
tests <- grouped_absolute_err %>%
  mutate(statistic = map2_dbl(.x = data, .y = data1, .f = function(x,y){
    DAAG::twotPermutation(x$abs_error, y$abs_error, nsim = 5000, plotit = FALSE)
    })
  )

```

We want to test for Eddy vs Shoreline in ABCD & HCP

## Permutation test results
```{r}
tests %>%
  select(-data, -data1) %>%
  knitr::kable()
```

```{r}

```


## T-test Results

```{r}
tests %>%
  filter_at(vars(contains("scheme")), any_vars(str_detect(., "HCP|ABCD"))) %>%
  filter_at(vars(contains("method")), any_vars(str_detect(., "eddy|SHORELine"))) %>%
  filter(was.moved == TRUE & was.moved1 == TRUE) %>%
  #filter(percent == percent1) %>%
  #filter(motion.type == motion.type1) %>%
  filter(scheme == scheme1) %>%
  filter(method != method1) %>%
  unite("scheme", contains("scheme"), sep = "_vs_") %>%
  unite("method", contains("_method"), sep = "_vs_") %>%
  mutate(n = rep(c(1,2), each = 2, times = nrow(.)/4)) %>%
  filter(n == 2) %>%
  select(-n) %>%
  set_names(~str_replace(., "x_", "")) %>%
  mutate(sig = p.value < 0.05/nrow(.)) %>% 
  select(p.value, sig, scheme:motion.type) %>%
  knitr::kable()
```

## Two Way Anova

We can use a traditional multiple anova between the groups:

```{r}
grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    aov(abs_error ~ scheme + method, data = .x) %>% 
      broom::glance()
    }, keep = TRUE) %>%
  mutate(sig = p.value < 0.05) %>%
  knitr::kable()
```

We can also get Tukey's adjusted HSD for multiple comparisons:

```{r}
grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    aov(abs_error ~ scheme * method, data = .x) %>% 
      TukeyHSD() %>%
      broom::tidy()
    }, keep = TRUE) %>%
  mutate(sig = adj.p.value < 0.05) %>%
  knitr::kable()
```

We can visualise each of the groups as well:

```{r}
means_moved <- grouped_absolute_err %>%
  filter(str_detect(scheme, "HCP|ABCD")) %>%
  filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    lm(abs_error ~ scheme * method, data = .x) %>% 
      emmeans(c("scheme", "method")) %>%
      broom::tidy()
    }, 
    keep = TRUE) %>%
  mutate(comparison = str_c(scheme, method, sep = ":")) %>%
  filter(was.moved == TRUE) %>%
  ggplot(aes(x=scheme, y=estimate)) +
    geom_col(aes(fill=method), position="dodge") +
    labs(y="marginal means") +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom") 
  
means_unmoved <- grouped_absolute_err %>%
  filter(str_detect(scheme, "HCP|ABCD")) %>%
  filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    lm(abs_error ~ scheme * method, data = .x) %>% 
      emmeans(., ~ scheme | method) %>%
      broom::tidy()
    }, 
    keep = TRUE) %>%
  mutate(comparison = str_c(scheme, method, sep = ":")) %>%
  filter(was.moved == FALSE) %>%
  ggplot(aes(x=scheme, y=estimate)) +
    geom_col(aes(fill=method), position="dodge") +
    labs(y="marginal means") +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom")

plot_grid(means_moved, means_unmoved, labels = c('Moved', 'Not Moved'), label_size = 12)
```

To show the differences between distributions of error, we can use violin plots like so:

```{r}
violins_moved <- grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  filter(was.moved == TRUE) %>%
  ggplot(aes(x=scheme, y=abs_error)) +
    geom_violin(aes(fill=method), position="dodge", draw_quantiles = TRUE) +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom",
          axis.text.x = element_text(angle = 90))

violins_unmoved <- grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  filter(was.moved == FALSE) %>%
  ggplot(aes(x=scheme, y=abs_error)) +
    geom_violin(aes(fill=method), position="dodge", draw_quantiles = TRUE) +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom",
          axis.text.x = element_text(angle = 90))

plot_grid(violins_moved, violins_unmoved, labels = c('Moved', 'Not Moved'), label_size = 12)
```



## How Do the different settings look for each method?
```{r}
ggplot(subset(settings.check, method=="3dSHORE"), aes(x=Estimated_Rigid, y=Estimated_Affine, color=scheme)) +
  geom_point() +
  facet_grid(motion.type ~ axis) +
  geom_abline()

ggplot(subset(settings.check, method=="eddy"), aes(x=Estimated_Linear, y=Estimated_Quadratic, color=scheme)) +
  geom_point() +
  facet_grid(motion.type ~ axis) +
  geom_abline()
```


```{r}
actually.moved <- subset(motion.check, was_moved)

ggplot(subset(actually.moved, percent_motion==15),
       aes(x=Truth, y=Estimated, color=method)) + 
  geom_point(alpha=0.2, shape=20) + 
  geom_abline(intercept=0, slope=1) +
  facet_grid(motion.type~ axis) +
  ggtitle("Estimated Motion vs. Ground Truth Motion (15% motion)")

ggplot(subset(actually.moved, percent_motion==33),
       aes(x=Truth, y=Estimated, color=method)) + 
  geom_point(alpha=0.2, shape=20) + 
  geom_abline(intercept=0, slope=1) +
  facet_grid(motion.type~ axis) +
  ggtitle("Estimated Motion vs. Ground Truth Motion (33% motion)")

```


## Compare absolute errors between the methods 

```{r}
library(viridis)
library(ggplot2)
library(cowplot)
library(extrafont)

loadfonts()
theme_set(theme_cowplot())
# Embed the fonts

comparable <- subset(motion_est_error, scheme %in% c('HCP', 'ABCD'))


ggplot(comparable, aes(x=scheme, y=value, fill=method, color=motion.type)) + 
  geom_boxplot(alpha=0.6)

#plot_grid(ss10, ss25, labels = c('A', 'B'), label_size = 12)
  

```



```{r}
comparable <- subset(actually.moved, scheme %in% c('DSIQ5', 'HASC55'))

ss10 <- ggplot(comparable, aes(x=error, fill=scheme)) + 
  geom_density(alpha=0.6, position="identity") +
  facet_grid(.~motion.type, scales = "free_y") 
# ss25 <- ggplot(subset(comparable, percent==25), aes(x=error, fill=scheme)) + 
#   geom_density(alpha=0.6, position="identity") +
#   facet_grid(.~motion.type, scales = "free_y") +
#   theme_cowplot(12)

#plot_grid(ss10, ss25, labels = c('A', 'B'), label_size = 12)
  

```