---
title: "Motion Estimation"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(viridis)
library(ggplot2)
library(cowplot)
library(extrafont)
library(reshape2)
library(ggplot2)
library(here)
library(emmeans)
library(DT)
library(patchwork)

library(tidyverse)
loadfonts()
```

## Estimating known motion

```{r read_results}
motion_df <- read.csv("data/motion_benchmark.csv")
qc_df <- read.csv('data/qc_benchmark.csv')

motion_df$was_moved <- !with(motion_df, 
  (true_trans_z == 0) &
  (true_trans_y == 0) &
  (true_trans_z == 0) &
  (true_rot_x == 0) &
  (true_rot_y == 0) & 
  (true_rot_z == 0))

table(motion_df$was_moved)

# Calculate the errors
for (motion_axis in c("x", "y", "z")){
  for (motion_type in c("trans", "rot")){
    est.mov.name <- paste0(motion_type, "_", motion_axis)
    est.mov <- motion_df[est.mov.name]
    if (motion_type == "rot"){
      est.mov <- est.mov * 180 / pi
      motion_df[est.mov.name] <- est.mov
    }
    true.mov <- motion_df[paste0("true_", motion_type, "_", motion_axis)]
    
    error.col <- paste("error", motion_type, motion_axis, sep="_")
    motion_df[error.col] <- true.mov - est.mov
  }
}

# Get only the columns for the motion analysis
motion_columns <- c("bval", "grad_x", "grad_y", "grad_z",
                    "iternum", "scheme", "method", "setting", "percent_motion", "was_moved",
                    "error_trans_x", "error_trans_y", "error_trans_z", "error_rot_x", "error_rot_y", "error_rot_z",
                    "true_trans_x", "true_trans_y", "true_trans_z", "true_rot_x", "true_rot_y", "true_rot_z",
                    "trans_x", "trans_y", "trans_z", "rot_x", "rot_y", "rot_z", "volnum"
                    )
moved <- motion_df[, motion_columns] %>%
  bind_cols(select(motion_df, matches("DWI")))


m.moved <- melt(moved,
    measure.vars = c("error_trans_x", "error_trans_y", "error_trans_z", "error_rot_x", "error_rot_y", "error_rot_z",
                     "true_trans_x", "true_trans_y", "true_trans_z", "true_rot_x", "true_rot_y", "true_rot_z",
                     "trans_x", "trans_y", "trans_z", "rot_x", "rot_y", "rot_z"))

m.moved$motion.type <- 'Translation'
m.moved$motion.type[grep('rot_', m.moved$variable)] <- 'Rotation'
table(m.moved$motion.type)
m.moved$axis <- gsub(".*_([xyz])$", '\\1', m.moved$variable)
m.moved$source <- "Estimated"
m.moved$source[grep('true', m.moved$variable)] <- "Truth"
m.moved$source[grep('error', m.moved$variable)] <- "Error"
table(m.moved$source)
motion_est_error <- subset(m.moved, source=="Error")
motion_ests <- subset(m.moved, source!="Error")
motion_ests$variable <- NULL
motion.check <- dcast(motion_ests, ... ~ source)
settings.check <- dcast(motion_ests, ... ~ source + setting)

```



## Estimating known motion

```{r cars}
truth <- moved %>%
  select(-matches('grad')) %>%
  select(-starts_with('error_')) %>%
  gather('truth', 'true_values', matches('true')) %>%
  select(-matches('_(x|y|z)'))
  
estimates <- moved %>%
  select(-matches('grad')) %>%
  select(-starts_with('error_')) %>%
  select(-starts_with('true_')) %>%
  gather('estimated', 'estimated_values', matches('_(x|y|z)'))
```



```{r estimated vs real motion plot}

# join the estimates and the true values
estimates2 <- estimates %>%
  bind_cols(select(truth, truth, true_values)) %>%
  # use only rows where there was actual perturbation
  filter(was_moved) %>%
  # get a column for the axis
  separate(estimated, into=c("motion_type", "axis"), sep="_") %>%
  mutate(percent_motion = as.factor(percent_motion))

# get the percentages
percents <- unique(estimates2$percent_motion) %>%
  sort()
settings <- unique(estimates2$setting)

# create a list for these
scatterplots <- vector("list", length = length(percents))

# start the ggplot
for(x in 1:length(percents)){
  
  estimates2 %>%
    filter(percent_motion == percents[x]) %>%
    filter(setting %in% c("Quadratic", "Affine")) %>%
    mutate(method = str_c(method, " (", setting, ")")) %>%
    ggplot(
      aes(x=true_values, 
          y=estimated_values, 
          color=method
          )
      ) +
    geom_point(shape=19, size=0.5, alpha = 0.2) + 
    geom_abline(intercept=0, slope=1) + 
    facet_grid(~motion_type, scales = "free") +
    theme_minimal() +
    ggtitle(#"Estimated Motion vs. Ground Truth Motion",
            paste0(percents[x], "% Motion")) +
    theme(legend.position = "bottom") +
    ylim(-10, 10) +
    guides(colour = guide_legend(override.aes = list(alpha = 1, size=1))) +
    theme_minimal() +
    theme(text = element_text(size=25)) -> scatterplots[[x]]

}


p <- wrap_plots(scatterplots, ncol = 1) + 
  guide_area() + 
  plot_layout(guides = 'collect') +
  plot_annotation(
  title = 'Comparing Estimated vs. True Motion of 3dSHORE & eddy',
  caption = 'Some more description can be put here')

p

ggsave("plot_outputs/estimate_v_true_motion.jpg", p, width = 14, height = 20)
```

```{r estimated vs real with scheme}
# get the percentages
percents <- unique(estimates2$percent_motion) %>%
  sort()
settings <- unique(estimates2$setting)

# create a list for these
scatterplots_abcd <- vector("list", length = length(percents))

# start the ggplot
for(x in 1:length(percents)){
  
  estimates2 %>%
    filter(percent_motion == percents[x]) %>%
    filter(setting %in% c("Quadratic", "Affine")) %>%
    filter(scheme == "ABCD") %>%
    mutate(method = str_c(method, " (", setting, ")")) %>%
    ggplot(
      aes(x=true_values, 
          y=estimated_values, 
          color=method
          )
      ) +
    geom_point(shape=19, size=0.3, alpha = 0.4) + 
    geom_abline(intercept=0, slope=1) + 
    facet_grid(~motion_type, scales = "free") +
    theme_minimal() +
    ggtitle(#"Estimated Motion vs. Ground Truth Motion",
            paste0(percents[x], "% Motion")) +
    theme(legend.position = "bottom") +
    ylim(-10, 10) +
    guides(colour = guide_legend(override.aes = list(alpha = 1, size=1))) +
    theme_minimal() +
    theme(text = element_text(size=22)) -> scatterplots_abcd[[x]]

}

# create a list for these
scatterplots_hcp <- vector("list", length = length(percents))

# start the ggplot
for(x in 1:length(percents)){
  
  estimates2 %>%
    filter(percent_motion == percents[x]) %>%
    filter(setting %in% c("Quadratic", "Affine")) %>%
    filter(scheme == "HCP") %>%
    mutate(method = str_c(method, " (", setting, ")")) %>%
    ggplot(
      aes(x=true_values, 
          y=estimated_values, 
          color=method
          )
      ) +
    geom_point(shape=19, size=0.3, alpha = 0.4) + 
    geom_abline(intercept=0, slope=1) + 
    facet_grid(~motion_type, scales = "free") +
    theme_minimal() +
    ggtitle(#"Estimated Motion vs. Ground Truth Motion",
            paste0(percents[x], "% Motion")) +
    theme(legend.position = "bottom") +
    ylim(-10, 10) +
    guides(colour = guide_legend(override.aes = list(alpha = 1, size=1))) +
    theme_minimal() +
    theme(text = element_text(size=22)) -> scatterplots_hcp[[x]]

}



p_abcd <- wrap_plots(scatterplots_abcd, ncol = 1) + 
  # guide_area() + 
  # plot_layout(guides = 'collect') +
  plot_annotation(
  title = 'ABCD Scheme')#,
#   caption = 'Some more description can be put here'
# )

p_hcp <- wrap_plots(scatterplots_hcp, ncol = 1) + 
  # guide_area() + 
  # plot_layout(guides = 'collect') +
  plot_annotation(
  title = 'HCP Scheme')#   caption = 'Some more description can be put here'
# )

p_scheme <- wrap_plots(p_abcd, p_hcp, ncol = 2) +
  guide_area() +
  plot_layout(guides = "collect") +
  plot_annotation(
  title = 'True vs Estimated Motion by Scheme',
  subtitle = "Left: ABCD\nRight: HCP", theme = theme(text = element_text(size=22)))

ggsave("plot_outputs/estimate_v_true_motion_scheme.jpg", p_scheme, width = 14, height = 20)
```


## Framewise Displacement

Let's calculate FD and visualise:

```{r}
power_fd <- function(data, radius=50, rotation_vars, translation_vars){
  
  stopifnot(
    is.list(rotation_vars),
    is.list(translation_vars)
  )
  
  df <- data

  # 1) multiply rotation columns by pi & / 180
  rotation_cols <- c("true_rot_x", "true_rot_y", "true_rot_z")
  back2radians <- data[, rotation_cols] * pi / 180.0
  # 
  back2radians2 <- data %>%
    select(!!!rotation_vars) %>%
    mutate(across(everything(), ~ .x * pi / 180.0))
  
  # 2) create a matrix of just translation cols and radians
  translation_cols=c("true_trans_x", "true_trans_y", "true_trans_z")
  motion_matrix <- cbind(df[, translation_cols], back2radians)
  motion_matrix2 <- data %>%
    select(!!!translation_vars) %>%
    bind_cols(back2radians)
  # 
  tdiff <- head(motion_matrix, -1) - tail(motion_matrix, -1)
  tdiff[, rotation_cols] <- tdiff[,c("true_rot_x", "true_rot_y", "true_rot_z")] * radius
  
  tdiff2 <- head(motion_matrix2, -1) - tail(motion_matrix2, -1) 
  
  times_rad <- function(x){
    
    return(x * radius)
  }
  
  tdiff2 <- tdiff2 %>%
    mutate(across(contains("rot"), times_rad))

  fd <- abs(tdiff)
  fd <- c( NA, rowSums(abs(tdiff)))
  # # Set the first volume to NA
  fd[df[,'volnum']==0] <- NA
  # return(fd)
  
  fd2 <- tdiff2 %>%
    mutate(across(everything(), ~ .x %>% abs())) %>%
    transmute(fd = select(., everything()) %>% rowSums()) %>%
    rbind(NA, .) %>%
    pull(fd) %>%
  return()
}

fd_col_actual <- power_fd(moved, 50, vars(true_rot_x, true_rot_y, true_rot_z), vars(true_trans_x, true_trans_y, true_trans_z))

fd_col_est <- power_fd(moved, 50, vars(rot_x, rot_y, rot_z), vars(trans_x, trans_y, trans_z))

motion_wfd <- moved %>%
  bind_cols(FD_actual = fd_col_actual, FD_est = fd_col_est) %>%
  mutate(FD_error = FD_est - FD_actual)

p1 <- motion_wfd %>%
  filter(was_moved == TRUE) %>%
  filter(scheme %in% c("ABCD", "HCP")) %>%
  mutate(method = str_c(method, " (", setting, ")")) %>%
  ggplot(aes(
    y = FD,
    x = scheme,
    color = method)) +
  geom_boxplot(alpha = 0.5, position = position_dodge(0.9))
  
percents <- unique(motion_wfd$percent_motion) %>%
  sort()

fdplots <- vector("list", length = length(percents))

# start the ggplot
for(x in 1:length(percents)){
  
  motion_wfd %>%
    filter(percent_motion == percents[x]) %>%
    filter(setting %in% c("Quadratic", "Affine")) %>%
    filter(!FD_actual == 0) %>%
    mutate(method = str_c(method, " (", setting, ")")) %>%
    ggplot(
      aes(x=FD_actual, 
          y=FD_est,
          color=method
          )
      ) +
    geom_point(alpha = 0.2, size=0.3) + #shape=19, size=0.0001, alpha = 0.2) +
    geom_abline(intercept=0, slope=1) + 
    # facet_grid(~motion_type, scales = "free") +
    theme_minimal() +
    ggtitle(#"Estimated Motion vs. Ground Truth Motion",
            paste0(percents[x], "% Motion")) +
    theme(legend.position = "bottom") +
    ylim(0, 40) +
    xlim(0, 40) +
    guides(colour = guide_legend(override.aes = list(alpha = 1, size=1))) +
    theme_minimal() -> fdplots[[x]]

}

p1 <- motion_wfd %>%
  # filter(percent_motion == percents[x]) %>%
  filter(setting %in% c("Quadratic", "Affine")) %>%
  filter(!FD_actual == 0) %>%
  mutate(method = str_c(method, " (", setting, ")")) %>%
  mutate(percent_motion = paste0(percent_motion, "% Motion")) %>%
  ggplot(
    aes(x=FD_actual, 
        y=FD_est,
        color=method
        )
    ) +
  geom_point(alpha = 0.2, size=0.7) + #shape=19, size=0.0001, alpha = 0.2) +
  geom_abline(intercept=0, slope=1) + 
  facet_grid(percent_motion~., scales = "free") +
  theme_minimal() +
  ggtitle('Comparing Estimated vs. True Framewise Displacement\nof 3dSHORE & eddy') +
  theme(legend.position = "bottom") +
  ylim(0, 40) +
  xlim(0, 40) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size=1))) +
  theme_minimal() +
  theme(text = element_text(size=23))

ggsave("plot_outputs/estimate_v_true_FD.jpg", p1, width = 14, height = 20)
# p1 <- wrap_plots(fdplots, ncol = 1) + 
#   guide_area() + 
#   plot_layout(guides = 'collect') +
#   plot_annotation(
#   title = 'Comparing Estimated vs. True Framewise Displacement\nof 3dSHORE & eddy',
#   # subtitle = 'Boxplots show distribution of data',
#   caption = 'Some more description can be put here'
# )
```

## Compare absolute errors between the methods

With patchwork:

```{r absolute error histogram}
actually.moved <- subset(motion.check, was_moved)

theme_set(theme_cowplot())
# Embed the fonts

actually.moved$error <- with(actually.moved, Truth - Estimated)
comparable <- subset(actually.moved, scheme %in% c('HCP', 'ABCD'))

# get the different percentages
percents <- unique(comparable$percent_motion) %>%
  sort()

# create a list for these
absolute_error_box <- vector("list", length = length(percents))

# for each of the percentages make a plot
for(x in 1:length(percents)){
  
  ptitle <- paste0(percents[x], "% Motion")
  
  pl <- comparable %>%
    filter(percent_motion==percents[x]) %>%
    filter(setting %in% c("Affine", "Quadratic")) %>%
    mutate(method = str_c(method, " (", setting, ")")) %>%
    # mutate(error = abs(error)) %>%
    # filter out the outlier who would normally be removed
    # filter(error < 20) %>%
    
    # start the ggplot
    ggplot(aes(x=scheme, y=error, fill=method)) + 
    geom_boxplot(width=0.9, position=position_dodge(1), outlier.alpha = 0.5, outlier.size = 0.5) +
    geom_hline(yintercept = 0) +
    facet_grid(~motion.type, scales = "free_y") +
    ylim(-8, 8) +
    coord_flip() +
    theme(legend.position = "bottom") +
    ggtitle(ptitle) +
    # theme_bw() +
    scale_fill_manual(values=c("#f0f0f0", "#636363"))

  
  absolute_error_box[[x]] <- pl
}

p2 <- wrap_plots(absolute_error_box, ncol = 1) + 
  guide_area() + 
  plot_layout(guides = 'collect') +
  plot_annotation(
  title = 'Error of Motion Correction for 3dSHORE & eddy',
  subtitle = 'Subset by % Motion',
  caption = 'Some more description can be put here'
)

ggsave("plot_outputs/motion_correction_error_boxpl.jpg", p2, width = 14, height = 16)
```

```{r absolute error density plot, include=FALSE, eval=FALSE}
comparable <- subset(actually.moved, scheme %in% c('DSIQ5', 'HASC55'))

# create a list for these
absolute_error_dens <- vector("list", length = length(percents))

percents <- unique(comparable$percent_motion)

# for each of the percentages make a plot
for(x in 1:length(percents)){
  
  ptitle <- paste0("Absolute Error of Motion Correction for ",
                  percents[x], "% Motion")
  pl <- comparable %>%
    # do the percent motion filter here
    filter(percent_motion==percents[x]) %>%
    
    # start the ggplot
    ggplot(aes(x=error, fill=scheme)) + 
      geom_density(alpha=0.6, position="identity") +
      facet_grid(.~motion.type, scales = "free_y") +
      theme_cowplot(12)
  
  absolute_error_dens[[x]] <- pl
}

plot_grid(plotlist = absolute_error_dens, labels = LETTERS[1:length(absolute_error_dens)], label_size = 12)

```

# Stat Tests

Here we test difference of variance between the absolute error of each parameter setting.

First, calculate absolute error for each estimation, then group by the parameters and nest this dataframe, giving one row of parameters with a nested df of absolute errors using these settings:
```{r include=FALSE, eval=FALSE}
grouped_absolute_err <- motion.check %>% 
  mutate(error = Estimated - Truth) %>% 
  mutate(abs_error =  abs(error)) %>%
  group_nest(scheme, method, percent_motion, was_moved, motion.type)

grouped_absolute_err <- grouped_absolute_err %>%
  filter(
    #scheme == scheme1 &
      method != method1 &
      percent == percent1 &
      was.moved == TRUE &
      was.moved1 == TRUE &
      motion.type == motion.type1
    ) %>%
  arrange_at(vars(-data, -data1))

grouped_absolute_err
```

Then, loop through each line of the absolute errors. For each line, compare the data using a nonparametric permutation T-test:
```{r, warning=FALSE, message=FALSE, cache=TRUE, include=FALSE, eval=FALSE}
tests <- grouped_absolute_err %>%
  mutate(statistic = map2_dbl(.x = data, .y = data1, .f = function(x,y){
    DAAG::twotPermutation(x$abs_error, y$abs_error, nsim = 5000, plotit = FALSE)
    })
  )

```

We want to test for Eddy vs Shoreline in ABCD & HCP

## Permutation test results
```{r, include=FALSE, eval=FALSE}
tests %>%
  select(-data, -data1) %>%
  knitr::kable()
```


## T-test Results

```{r, include=FALSE, eval=FALSE}
tests %>%
  filter_at(vars(contains("scheme")), any_vars(str_detect(., "HCP|ABCD"))) %>%
  filter_at(vars(contains("method")), any_vars(str_detect(., "eddy|SHORELine"))) %>%
  filter(was.moved == TRUE & was.moved1 == TRUE) %>%
  #filter(percent == percent1) %>%
  #filter(motion.type == motion.type1) %>%
  filter(scheme == scheme1) %>%
  filter(method != method1) %>%
  unite("scheme", contains("scheme"), sep = "_vs_") %>%
  unite("method", contains("_method"), sep = "_vs_") %>%
  mutate(n = rep(c(1,2), each = 2, times = nrow(.)/4)) %>%
  filter(n == 2) %>%
  select(-n) %>%
  set_names(~str_replace(., "x_", "")) %>%
  mutate(sig = p.value < 0.05/nrow(.)) %>% 
  select(p.value, sig, scheme:motion.type) %>%
  knitr::kable()
```

## Two Way Anova

We can use a traditional multiple anova between the groups:

```{r, include=FALSE, eval=FALSE}
grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    aov(abs_error ~ scheme + method, data = .x) %>% 
      broom::glance()
    }, keep = TRUE) %>%
  mutate(sig = p.value < 0.05) %>%
  knitr::kable()
```

We can also get Tukey's adjusted HSD for multiple comparisons:

```{r, include=FALSE, eval=FALSE}
grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    aov(abs_error ~ scheme * method, data = .x) %>% 
      TukeyHSD() %>%
      broom::tidy()
    }, keep = TRUE) %>%
  mutate(sig = adj.p.value < 0.05) %>%
  knitr::kable()
```

We can visualise each of the groups as well:

```{r, include=FALSE, eval=FALSE}
means_moved <- grouped_absolute_err %>%
  filter(str_detect(scheme, "HCP|ABCD")) %>%
  filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    lm(abs_error ~ scheme * method, data = .x) %>% 
      emmeans(c("scheme", "method")) %>%
      broom::tidy()
    }, 
    keep = TRUE) %>%
  mutate(comparison = str_c(scheme, method, sep = ":")) %>%
  filter(was.moved == TRUE) %>%
  ggplot(aes(x=scheme, y=estimate)) +
    geom_col(aes(fill=method), position="dodge") +
    labs(y="marginal means") +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom") 
  
means_unmoved <- grouped_absolute_err %>%
  filter(str_detect(scheme, "HCP|ABCD")) %>%
  filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  group_by(percent, was.moved, motion.type) %>%
  group_modify( ~ {
    lm(abs_error ~ scheme * method, data = .x) %>% 
      emmeans(., ~ scheme | method) %>%
      broom::tidy()
    }, 
    keep = TRUE) %>%
  mutate(comparison = str_c(scheme, method, sep = ":")) %>%
  filter(was.moved == FALSE) %>%
  ggplot(aes(x=scheme, y=estimate)) +
    geom_col(aes(fill=method), position="dodge") +
    labs(y="marginal means") +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom")

plot_grid(means_moved, means_unmoved, labels = c('Moved', 'Not Moved'), label_size = 12)
```

To show the differences between distributions of error, we can use violin plots like so:

```{r, include=FALSE, eval=FALSE}
violins_moved <- grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  filter(was.moved == TRUE) %>%
  ggplot(aes(x=scheme, y=abs_error)) +
    geom_violin(aes(fill=method), position="dodge", draw_quantiles = TRUE) +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom",
          axis.text.x = element_text(angle = 90))

violins_unmoved <- grouped_absolute_err %>%
  #filter(str_detect(scheme, "HCP|ABCD")) %>%
  #filter(str_detect(method, "eddy|SHORELine")) %>%
  unnest(data) %>%
  filter(was.moved == FALSE) %>%
  ggplot(aes(x=scheme, y=abs_error)) +
    geom_violin(aes(fill=method), position="dodge", draw_quantiles = TRUE) +
    facet_grid(rows = vars(percent), cols = vars(motion.type)) +
    theme(plot.margin = unit(c(1,0.5,0.5,0.5), "cm"), legend.position = "bottom",
          axis.text.x = element_text(angle = 90))

plot_grid(violins_moved, violins_unmoved, labels = c('Moved', 'Not Moved'), label_size = 12)
```



## How Do the different settings look for each method?
```{r, include=FALSE, eval=FALSE}
ggplot(subset(settings.check, method=="3dSHORE"), aes(x=Estimated_Rigid, y=Estimated_Affine, color=scheme)) +
  geom_point() +
  facet_grid(motion.type ~ axis) +
  geom_abline()

ggplot(subset(settings.check, method=="eddy"), aes(x=Estimated_Linear, y=Estimated_Quadratic, color=scheme)) +
  geom_point() +
  facet_grid(motion.type ~ axis) +
  geom_abline()
```


```{r, include=FALSE, eval=FALSE}
actually.moved <- subset(motion.check, was_moved)

ggplot(subset(actually.moved, percent_motion==15),
       aes(x=Truth, y=Estimated, color=method)) + 
  geom_point(alpha=0.2, shape=20) + 
  geom_abline(intercept=0, slope=1) +
  facet_grid(motion.type~ axis) +
  ggtitle("Estimated Motion vs. Ground Truth Motion (15% motion)")

ggplot(subset(actually.moved, percent_motion==33),
       aes(x=Truth, y=Estimated, color=method)) + 
  geom_point(alpha=0.2, shape=20) + 
  geom_abline(intercept=0, slope=1) +
  facet_grid(motion.type~ axis) +
  ggtitle("Estimated Motion vs. Ground Truth Motion (33% motion)")

```


## Compare absolute errors between the methods 

```{r, include=FALSE, eval=FALSE}
library(viridis)
library(ggplot2)
library(cowplot)
library(extrafont)

loadfonts()
theme_set(theme_cowplot())
# Embed the fonts

comparable <- subset(motion_est_error, scheme %in% c('HCP', 'ABCD'))


ggplot(comparable, aes(x=scheme, y=value, fill=method, color=motion.type)) + 
  geom_boxplot(alpha=0.6)

#plot_grid(ss10, ss25, labels = c('A', 'B'), label_size = 12)
  

```



```{r, include=FALSE, eval=FALSE}
comparable <- subset(actually.moved, scheme %in% c('DSIQ5', 'HASC55'))

ss10 <- ggplot(comparable, aes(x=error, fill=scheme)) + 
  geom_density(alpha=0.6, position="identity") +
  facet_grid(.~motion.type, scales = "free_y") 
# ss25 <- ggplot(subset(comparable, percent==25), aes(x=error, fill=scheme)) + 
#   geom_density(alpha=0.6, position="identity") +
#   facet_grid(.~motion.type, scales = "free_y") +
#   theme_cowplot(12)

#plot_grid(ss10, ss25, labels = c('A', 'B'), label_size = 12)
  

```